\documentclass{report}

\author{Carsten Lemmen}
\title{GLUES visualization handbook}

\newcommand{\code}[1]{\verb|#1|}

\begin{document}
\maketitle

\chapter{Matlab}


\section{Basic mapping}

\subsection{The \code{m_map} package}

The freely available \code{m_map} package is required for full functionality of all map visualization in the GLUES package.  You can download this package 
at.  

\subsection{Creating a base map}
With the procedure \code{clp_basemap}, a world map between -60 N and 70 N latitude is drawn with coast lines in blue color.

\subsection{Overlaying a picture of Earth}
The view of Earth as seen from space is commonly termed the ``Blue Marble''.  Pictures of this blue marble are available from NASA or from TrueMarble.
The procedure \code{clp_marble} automatically downloads a background picture from the internet and overlays the base map with this image of vegetation and ice cover.

\section{Library functionality}
All utility functions are separated from the end user functions in a subdirectory \code{lib}.  

\subsection{Startup}
When started from the local directory, the \code{startup} program is run automatically by Matlab.  If not, you should call this program manually, it adds the local directory and its subdirectories to the Matlab search path.

\subsection{Logging}
A logging facility is provided by \code{cl_register_function}.  Each routine registers itself with this function when it is called.  All calls are written to the journal
file \code{journal.txt}.

\end{document}
